---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# reliabilitydiag

This package implements reliability diagrams via the CORP approach, which generates provably statistically Consistent, Optimally binned, and Reproducible reliability diagrams in an automated way.

CORP is based on non-parametric isotonic regression and implemented via the Pool-adjacent-violators (PAV) algorithm - essentially, the CORP reliability diagram shows the graph of the PAV- (re)calibrated forecast probabilities. The CORP approach allows for uncertainty quantification via either resampling techniques or asymptotic theory, furnishes a new numerical measure of miscalibration, and provides a CORP based Brier score decomposition that generalizes to any proper scoring rule.

## Installation

```{r, eval = FALSE}
# Install development version from GitHub
devtools::install_github("aijordan/reliabilitydiag")
```

## Example

```{r example}
library(reliabilitydiag)
data("precip_Niamey_2016", package = "reliabilitydiag")

X <- precip_Niamey_2016$EMOS
Y <- precip_Niamey_2016$obs
reliabilitydiag(EMOS = X, y = Y)
```

